Timeliness of security updates for Android

### 2014-02-18 securityupdates.tex
Add missing references on proportion of malware with root exploits
Adjust preamble to use macros for variables we might change

\newcommand{\percArdMarketShare}{XX\%}
\newcommand{\percArdInsec}{XX\%}
\newcommand{\percCrmMarketShare}{XX\%}
\newcommand{\percCrmInsec}{X\%}
\newcommand{\daNumManufacturers}{XX}
\newcommand{\daNumNetworkOperators}{XXX}

@@

\section{Introduction}
Android has XX\% of the smartphone market~\cite{TODO} and while the core development is controlled by Google there are at least XX~\cite{TODO} manufacturers which make devices which run Android.
Many of these manufacturers customise the version of Android they ship and sometimes network operators (of which there are at least XX~\cite{TODO}) make further modifications.
Hence when Google produces an update to Android, the update may have to pass through the manufacturer and operator before reaching the user.
The manufacturer and user have no financial incentive to perform this work.
There is ongoing legal action to force some of them to do so~\cite{Soghoian2013}.
CESG which advises the UK government on how to secure its computer system recommends picking Android devices from manufactures which are good at shipping security updates promptly~\cite{CESG2013} but it does not state which manufacturers are better.

Android relies on the Linux kernel to provide compartmentalisation and runs each app as a separate unix `user'.
The Linux kernel is a large piece of software and so there will always be new root exploits found in it~\cite{TODO}.
Manufacturers of Android devices have also added further root exploits when customising it~\cite{TODO}.
Between XX\%~\cite{TODO} and XX\%~\cite{TODO} of malware for Android contains root exploits.
While this shows that much Android malware does not need a root exploit to work, it can just request the relevant permissions and the user will grant them, a significant proportion does.
This malware is also more dangerous because while ordinary malware can be remotely removed by Google through the Play store, once a root exploit has been used there are no guarantees.

>>>>

\newcommand{\percMarketShare}{XX\%~\cite{TODO}}
\newcommand{\percInsec}{XX\%~\cite{TODO}}
\newcommand{\daNumManufacturers}{XX~[\S\ref{sec:results}]}
\newcommand{\daNumNetworkOperators}{XXX~[\S\ref{sec:results}]}

@@

\section{Introduction}
Android has \percMarketShare of the smartphone market and while the core development is controlled by Google there are at least \daNumManufacturers manufacturers which make devices which run Android.
Many of these manufacturers customise the version of Android they ship and sometimes network operators (of which there are at least \daNumNetworkOperators) make further modifications.
Hence when Google produces an update to Android, the update may have to pass through the manufacturer and operator before reaching the user.
The manufacturer and user have no financial incentive to perform this work.
There is ongoing legal action to force some of them to do so~\cite{Soghoian2013}.
CESG which advises the UK government on how to secure its computer system recommends picking Android devices from manufactures which are good at shipping security updates promptly~\cite{CESG2013} but it does not state which manufacturers are better.

Android relies on the Linux kernel to provide compartmentalisation and runs each app as a separate unix `user'.
The Linux kernel is a large piece of software and so there will always be new root exploits found in it~\cite{TODO}.
Manufacturers of Android devices have also added further root exploits when customising it~\cite{TODO}.
Between 36.7\%~\cite{Zhou2012b} and 40\%~\cite{Zhou2012a} of malware for Android contains root exploits.
While this shows that much Android malware does not need a root exploit to work, it can just request the relevant permissions and the user will grant them, a significant proportion does.
This malware is also more dangerous because while ordinary malware can be remotely removed by Google through the Play store, once a root exploit has been used there are no guarantees.
